The Perils of Exploration under Competition: \\ A Computational Modeling Approach

### 2020-07-09 journal paper/ec19paper/content/perf_in_iso.tex
updated performance in isolation figures to be PDF + slightly nicer

\begin{figure}
\centering
\includegraphics[scale=0.3]{ec19paper/figures/nih_iso_mean}
\includegraphics[scale=0.4]{ec19paper/appendix_figures/uniform_mean}
%\caption*{\tiny{Mean reputation trajectory The plots contain the average reputation over $1000$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of a given algorithm on a given instance and then average this value across all the runs. The shaded area display 95\% confidence intervals.}}
\caption{Mean reputation trajectories for Needle-in-Haystack and Uniform. The shaded area shows 95\% confidence intervals.}
\label{prelim_means}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[scale=0.35]{ec19paper/figures/relative_uniform_annotated_plot}
\includegraphics[scale=0.35]{ec19paper/figures/relative_nih_ts_dg.png}
%\caption*{\tiny{The plots contain the average reputation over $1000$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of both of the algorithms on a given instance and then calculate the proportion of runs where $\TS \geq \DG$. The shaded area display 95\% confidence intervals.}}
\caption{Relative reputation trajectory for $\TS$ vs $\DG$, on Uniform instance (top) and Needle-in-Haystack instance (bottom). Shaded area display 95\% confidence intervals.}
\label{relative_rep_plots}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.35]{ec19paper/figures/nih_iso_mean}
\includegraphics[scale=0.35]{ec19paper/figures/uniform_mean}
%\caption*{\tiny{Mean reputation trajectory The plots contain the average reputation over $1000$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of a given algorithm on a given instance and then average this value across all the runs. The shaded area display 95\% confidence intervals.}}
\caption{Mean reputation trajectories for Needle-in-Haystack and Uniform. The shaded area shows 95\% confidence intervals.}
\label{prelim_means}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[scale=0.35]{ec19paper/figures/relative_uniform_annotated_plot}
\includegraphics[scale=0.35]{ec19paper/figures/relative_nih_ts_dg}
%\caption*{\tiny{The plots contain the average reputation over $1000$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of both of the algorithms on a given instance and then calculate the proportion of runs where $\TS \geq \DG$. The shaded area display 95\% confidence intervals.}}
\caption{Relative reputation trajectory for $\TS$ vs $\DG$, on Uniform instance (top) and Needle-in-Haystack instance (bottom). Shaded area display 95\% confidence intervals.}
\label{relative_rep_plots}
\end{figure}
